\documentclass[white]{gl2018}

\begin{document}
\name{\wWinterRitual{}}
\begin{center}
\section*{Research Results: How do we return the University to the mortal world?}
\end{center}

{\bf This document contains spoilers; if you wish to avoid spoilers about the climax of the game, ask someone to read it to you, skipping the spoilers, or ask a GM for help.}

This massive task will require a ritual. A ritual like this has never been performed before, as there has never been such a need. \emph{(OOG: The details of the ritual are at the players’ discretion).} Your research suggests a couple of requirements, and a couple of recommendations however:
\begin{enumerate}
\item Required:
\begin{itemize}
\item The ritual must take place at a time when one or more of the involved keepers are distracted.
\begin{itemize}
\item (OOG NOTE {\bf containing spoilers:} The necessary condition for the ritual will exist during the climax of the game, and offers a non-combat alternative for players who wish to participate in a world impacting plot without engaging in the final combat mechanic.)
\end{itemize}
\item The ritual requires massive power. Ideally, it is powered by the protective contracts of the University. Failing contracts (i.e.: one that remains unfulfilled) do not have enough power. Enough power to substitute for them may be acquired by a character volunteering to give up their life’s energy to power the ritual (their character will die at end of game). More than one of the contracts may be substituted in this manner if enough volunteers can be found.
\item If the ritual is underpowered, the ritual will return the University to the mortal world just long enough for characters to escape if player wish for them to do so, after which, this portion of the University will likely be lost forever.
\end{itemize}
\item Recommendations:
\begin{itemize}
\item Include some contribution from all four courts and/or the four contracts.
\item Include a way for each player to participate in a unique manner, such as sharing a memory with the group, or sacrificing something important to power the effect.
\item You may find it difficult to sustain compelling role play for more than about 30 minutes, depending on the elaborateness of the ritual, and the number of participants. 
\begin{itemize}
\item (OOG NOTE {\bf containing spoilers:} You will have up to 2 hours to prepare and execute the ritual during the climax of game. Ideally this ritual and the final combat end at roughly the same time. If you end the roleplaying portion of the ritual before the final combat is concluded, you may join the combat, or watch the combat from OOC.)
\end{itemize}
\end{itemize}
\end{enumerate}

\subsection*{Additional Benefit - Immediate Action Required}
\underline{{\bf Heal -}} by uncovering what happened to the University, and a way to heal it, you have learned something about how to heal each other, and now have access to a new action for the final battle: ``Heal''. Announce this on the $\langle$ooc channel$\rangle$ immediately.
\end{document}
