\documentclass[white]{gl2018}
\begin{document}
\name{\wResearchForm{}}
\begin{center}\section*{Research Submission Form}\end{center}

{\large Topic or Question to Research:}\line(1,0){275}\\
Date submitted:  \line(1,0){275}\\
Time submitted:  \line(1,0){275}\\

\emph{{\bf Research requires a minimum of 2 Researchers.} All listed researchers will receive an electronic copy of the research results once it is complete. Some research may also yield hard copies of the results.}\\
Researcher(s):\\
\line(1,0){275} \\
\line(1,0){275} \\
\line(1,0){275} \\
\line(1,0){275} \\

\emph{Research takes 8 hours to complete by default. The minimum research time is 4 hours. Use the following section to calculate the amount of time your research will actually take.}
\begin{itemize} 
	\item If any researcher has Wyrd $\le 4$, reduce research time by 2 hours.  Put that researcher's name here:
	\item\line(1,0){275}
	\item For each additional researcher beyond 2, reduce the time by half an hour (30 min) to a minimum of 4 hours. If the head librarian is one of the researchers, she reduces the time by 1 hour instead of 30 minutes. Total time reduction based on additional researchers:
	\item\line(1,0){275}
\end{itemize}
Amount of time research will take: \line(1,0){275}\\
\emph{Minimum research time is 4 hours}

\emph{Once you have completed this form, drop it in the envelope attached to the ``\sResearchFormSubmission{\MYname{}}'' sign, send the GMs a message on Discord so there's no delay in us getting to work preparing your findings, and await your results.}

{\it GMs may further reduce research time at their discretion.}
\end{document}
