\documentclass[white]{gl2018}

\begin{document}
\name{\wWinterRitual{}}
\begin{center}
\section*{Research Results: How can we communicate with the fog?}
\end{center}
\subsection*{Introduction}
The gremlins are very excited as they hand over a page of notes that look like they were painstakingly copied by an 8 year old. ``Ancient books'' they say. ``Missing from the library, now found. Soon lost again.'' and they run off, as gremlins are wont to do.

\subsection*{The Ritual}
\emph{{\bf Notify a GM at least 10 minutes before attempting this ritual.}}\\
\emph{This ritual has plenty of room for player creativity to add parts, and provide feel and flavor, but below we outline the minimum requirements:}
\begin{enumerate}
\item Gather at least 1 representative from each court. (more may be present, but this is the minimum.) Message the GMs if one is not already present.
\item Characters must enact a summoning ritual. It maybe of your own design, and as involved as you like, or you may use the default: All present must recite: ``We call to the fog. / That which blankets the university. / Our shield and our stealth, / we evoke our right as Chione’s children that we may speak to you.''
\item A winter courtier must lend the fog some of their power by losing 1 wyrd. If a courtier from another court tries this, nothing will happen, and their Wyrd is returned to them.
\item The fog will manifest and you will be able to converse with it.
\item When you end the ritual (again, it is up to the players how elaborate ending the ritual is), the courtier who led the ritual gains 2 Wyrd.
\end{enumerate}

\emph{This ritual may be enacted more than once, but after the first time, a second mechanic will be made known to the leadership of the Winter Court.}

\subsection*{Additional Benefit - Immediate Action Required}
\underline{{\bf Flank - }}by uncovering this lost aspect of university history, players now have the aid of the fog, and access to a new action for the final battle: “Flank”. Announce this on the $\langle$ooc channel$\rangle$ immediately
\end{document}
