\documentclass[green]{gl2018}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\begin{document}
\name{\gInvestigateTheMap{}}



\emph{{\bf If you are looking at this page, you must message the GMs on Discord and let them know.}}

Some quick investigating uncovers that this map it is an artifact designed to accurately render the location of the University along the dimentional axes that define the separation between the mortal world and Arcadia. It was created by an Autumn Courtier in the 1960s, and while generally considered a great feat of magic, has never had much practical use. The University does tend to wander a bit, sometimes drifting closer to the hedge, other times more firmly grounded in the mortal world. There are some weak trends, argued by a few academics, that the position of the University correlates with the density of the fog. The University is supposedly closer to the hedge when the fog is heavier.

\vspace{25px}
\emph{{\bf How to continue with this plot:}}
\begin{changemargin}{2cm}{2cm}
 Investigate the fog by going out to the lower meadow, and exploring. We recommend you take other characters with you and use this as an opportunity for role playing and involving other people in this plot. You may interact with the fog mechanic (recommended), or role-play other exploration. If you spend enough time in the fog (20 minutes), you may open the ``R packet'' inside the orange game materials source box out there.
\end{changemargin}

\end{document}
