\documentclass[green]{gl2018}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\begin{document}
\name{\gReflectingPool{}}

\section*{Instructions}
Whether through trial and error, or because you come forearmed with the knowledge of how to use the pool, you follow the below steps and experience the following:
	\begin{enumerate}
		\item {\bf Drink from the pool:} The water tastes bitter and metallic, and so cold it burns all the way down, before finally hitting your stomach like a weight. Your throat and mouth are numb and tingly, and you suddenly feel dizzy and disoriented. 
		\item {\bf Douse your protective candle,} or don’t have it lit to begin with.
		\item {\bf Gaze into the pool:} Your dark silhouette, both eerily familiar and undeniably alien, stares back at you, framed by sooty grey sky and trees. The hairs on the back of your neck rise as foreboding creeps over you, yet you cannot tear your gaze away. Your head is swimming, the world around the pool blurring and fading, until it is only you and the dark world waiting just beneath the surface of the water. Then even that blurs and shifts, reforming into a vision before your eyes. 
		\item {\bf You see a Vision of Terror.} If this is your first time using the pool, select option (a) below. If you have used the pool before, choose any one of the three options below:
		\begin{enumerate}
			\item {\bf Let the pool decide what to show you:} Open the top envelope in the stack labeled ``\mPoolVisionOne{}'' at this location, read the contents, then return it to the bottom of the stack. If you draw a vision you’ve already seen, you may place it at the bottom of the stack and draw a new one.
			\item {\bf Make up a vision OOC} pertaining to one of your personal or faction plots. This can be a great way to get personal/faction secrets into game.
			\item {\bf Force the pool to answer a particular question} that you do not have an answer to OOC. Notify a GM of the question, and you will receive an answer back with what you see. Your character will pay a higher price for this option.
			\end{enumerate}
		\item {\bf Increase your $\Psi$ (Psi) Score by 3.}
		\item {\bf The Vision of Terror ends} and your dark reflection returns. With a creeping dread, it dawns on you that your shadow self is gazing back at you, piercing to your very soul, with a will of its own. If you try to turn away, your body remains motionless, for it no longer answers to you. The shadow raises its arms, reaching towards you, and your own arms mirror its motion like a puppet. Your fingertips meet at the water’s surface, sending ripples exploding outwards. When they clear, you see your shadow doppelganger framed by green trees, and realize with horror that now {\bf you} are the one looking from beneath the surface of the water. With a mocking smile, the shadow turns away from the pool, leaving you screaming silently beneath the dark waters. 
		\item {\bf The inversion:} You continue to play your character, but your personality, beliefs, and goals temporarily transform into their opposites, and when this effect wears off, you retain {\bf no memory} of your actions subsequent to the Vision of Terror. While your personality is inverted, any attempt to use the pool yields no results. To determine duration of the inversion, consult the table on the following page. If you chose option (4)(c) above (forcing the pool to answer a particular question), however, {\bf double the duration} provided in the table. If you would like to avoid seeing the full duration table to preserve the OOC suspense of future uses, feel free to message the GMs to ask for your duration or ask another player to check it for you.
	\end{enumerate}
	
	\section*{Duration Table}
	Find the duration corresponding to your Wyrd stat and the number of times you have used the pool in the table below. Remember, if you forced the pool to answer a particular question, {\bf double} the duration provided in the table.
	
	\begin{center}
  \begin{tabular}{ | c | c | c | c | c | c |}
    \hline
    {\bf No. of pool uses:} & 1 & 2 & 3 & 4 & 5 \\ \hline
		{\bf Wyrd} & \multicolumn{5}{|c|}{{\bf Duration in Minutes}} \\ \hline
    {\bf 0} & 5 & 10 & 20 & 40 & 80 \\ \hline
		{\bf 1} & 6 & 12 & 24 & 48 & 96 \\ \hline
		{\bf 2} & 7 & 14 & 28 & 56 & 112\\ \hline
		{\bf 3} & 8 & 16 & 32 & 64 & 128 \\ \hline
		{\bf 4} & 9 & 18 & 36 & 72 & 144 \\ \hline
		{\bf 5} & 10 & 20 & 40 & 80 & 160 \\ \hline
		{\bf 6} & 11 & 22 & 44 & 88 & 176 \\ \hline
		{\bf 7} & 12 & 24 & 48 & 96 & 192 \\ \hline
		{\bf 8} & 13 & 26 & 52 & 104 & 208 \\ \hline
		{\bf 9} & 14 & 28 & 56 & 112 & 224 \\ \hline
		{\bf 10} & 15 & 30 & 60 & 120 & 240 \\ 
    \hline
  \end{tabular}
\end{center}

\end{document}
