\documentclass[green]{gl2018}
\begin{document}
\name{\gResearchForm{}}

\emph{All listed researchers will receive an electronic copy of the research results once it is complete.}\\
Name of Lead Researcher:\\
Name of Additional Researchers:\\

Topic or Question to Research:\\
Date submitted:\\
Time submitted:\\

\emph{Research takes 8 hours to complete by default. Use the following section to calculate the amount of time your research will actually take.}
\begin{itemize}
\item What is the Lead Researcher's Wyrd:  
\begin{itemize} \item If the Lead Researcher's Wyrd less than or equal to 4, reduce research time by 2 hours. \end{itemize}
\item Have the library gremlins been convinced to help you? (there is a specific mechanic in the library to try to convince the gremlins to help you.) If they are indeed helping your perform your research, reduce research time by 1 hour.
\item Are you expending any abilities that reduce the research time? If so, reduce the time by the appropriate amount and write the abilities below:
\begin{itemize}
\item Ability (Research duration reduction):
\item Ability (Research duration reduction):
\item Ability (Research duration reduction):
\end{itemize}
\end{itemize}

Amount of time research will take:

\emph{Once you have completed this form, drop it in the envelope attached to the ``\sResearchSubmission{\MYname}'' sign, send the GMs a message on Discord so there's no delay in us getting to work preparing your findings, and await you results.}

\end{document}
