\documentclass[green]{gl2018}
\usepackage{scrextend}
\begin{document}
\name{\gTrod{}}
\newcommand{\areastart}[1]{ \begin{huge}{\bf \#{#1}} \end{huge} \\}
\newenvironment{sect}[1]{\begin{minipage}{\textwidth}\areastart{#1}\\}{\end{minipage}\vspace{2in}}

Follow the instructions in the player system doc, duplicated here for your convenience:
\begin{addmargin}[0.5in]{0em}

\subsection*{Using the Trod}

Game space contains one trod (a doorway between the mortal world and the hedge). To use the trod (in either direction), go to the two white incense burners in front of the garden in the middle of the asphalt outside the dining hall. If you want to, and are able, walk up the steps from the asphalt, between the two burners. Stop, turn around, and pass back between the burners as you descend the stairs to the asphalt. If you can’t, or don’t want, to climb the stairs, just declare your intent to use the Trod. Check your watch and note the time, then proceed as follows.
\end{addmargin}
Find the first condition that matches the time you passed between the incense burners, turn to that number, and do what it says. {\em Do not look at any other items.}
\begin{enumerate}
\item If the time is before 10 am on Saturday, Oct 27th, including any time on Friday, go to \#1.
\item 
If the time includes at least 2 zeros (i.e.: 1\textbf{0:0}4, 3:\textbf{00}), go to \#2.
\end{enumerate}
\item If the hour includes 2 digits, (i.e.: \textbf{10}:32, \textbf{12}:14 but not \textbf{2}:40), go to \#3.
\item 
If the time includes at least one 4 (i.e.: \textbf{4}:\textbf{4}8, 9:\textbf{4}2), go to \#4.
\item 
If the last digit in the time is divisible by three (i.e: 1:0\textbf{3}, 3:1\textbf{9}), go to \#5.
If the hours digit is even (i.e: 2:01, 8:30), turn to page 7.
If the last digit is 5, (i.e: 1:55, 7:25), turn to page 8. 
If the tens digit of the minutes is odd (i.e.: 9:37, 5:18), turn to page 9.
If the last digit is prime (i.e:7:27, 5:02; note that neither 0 nor 1 are prime), turn to page 10 .
If the hours digit is composite, (i.e: 9:20, 9:28), turn to page 11.
If the time includes at least one 1 (i.e.: 1:08, 5:21), turn to page 12.
If the hours digit digit is odd (i.e: 3:28, 7:20), turn to page 13.

\pagebreak
\end{document}
