\documentclass[green]{gl2018}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\begin{document}
\name{\gYanoraManuscript{}}



\emph{{\bf If you are looking at this page, you must message the GMs on Discord and let them know.}}

\emph{The manuscript begins:}
\begin{changemargin}{3cm}{3cm}
We are all intimately familiar with the Oath of Red Branches, and the Brazen Pledge, and at least somewhat familiar with the Galena Compact. What modern scholars are too quick to dismiss is the possibility that we do not know the whole story of the founding contracts. Several crucial parts of the story are not adequately explained with only three contacts. The founding of the University on the Quarter System, references in Piper’s early notes about Linden Wax that suggest to the astute linguist that he did not arrive alone, and the absence of a counterbalance to the Brazen Pledge among them.
\end{changemargin}

The article ultimately makes a bold claim that there are in fact 4 founding contacts, and that the Winter Court has simply refused to tell the world for a hundred years. You can see for yourself that the article lacks any hard evidence that this is the case, but the author is adamant that if {\bf Brendan Cloche’s lost diary}could be found, it would prove the author right.

While several references in the article mention the diary, it seems to be long lost. However, the diary lock and its associated {\bf key} were apparently forged in France before the turn of the century, out of star-metal. Star-metal is attracted to itself, and so if the key could be found, it could be used to find the diary. Common wisdom holds that Brendan kept the key with him at all times. If that is true, the key would have been lost in the firing of the great bell of Cloche Tower.

\vspace{25px}
\emph{How to continue with this plot:}
\begin{changemargin}{3cm}{3cm}
If you wish to further investigate {\bf the key to Brendan Cloche’s diary}, head to Cloche Tower, and search for it. This item will not be findable until Saturday morning.
\end{changemargin}

\end{document}
